---
title: "Demo analysis"
output: github_document
---

This is the demo analysis.

The first thing to do is have setup block. This block is for:

- Setting code environment
- Load libraries
- Setting parameters


```{r setup, include=FALSE}
library(tidyverse)
library(knitr)
knitr::opts_chunk$set(echo=FALSE)
```

## This is the first section

You can print pretty tables using `knitr::kable()` 

```{r show-head}
mtcars |>
  select(mpg) |> 
  head() |>
  kable()

```
Most times we want visualizations to tell us more stories or insights regarding the data collected.


```{r mtcars-mpg-histgg-plot, message=FALSE}
mtcars %>%
  mutate(mpg = mpg / 10) %>%
  filter(mpg < 100) %>%
  select(mpg) %>%
  ggplot(aes(x=mpg)) +
  geom_histogram(fill="lightblue", col="black") +
  theme_bw()  +
  labs(x = "Miles per Gallon", y = "Count")
```

This plot shows the miles per gallon distribution in the `mtcars` dataset. 


```{r mtcars-mpg-hist-baseR-plot}
mtcars %>% 
  select(mpg) %>%
  pull() %>%
  hist(col = "lightblue")


```


## This should be another section

Now, we could fit a line of best fit to the plot (when they're scatterplots).

```{r mtcars-mpg-disp-scatter-plot, message=FALSE}
mtcars %>%
  select(mpg, disp) %>%
  ggplot(aes(x=mpg, y=disp)) +
  geom_point(col = "red" , size=2) +
  geom_smooth(method="lm") +
  theme_bw()

```